Evaluating the Effects of Tracker Reliability and Field of View on a Target Following Task in Augmented Reality

### 2009-06-25 trunk/Paper/paper.tex

\title{A Study of an X-Ray Vision Tracking Task in Simulated Augmented Reality}

@@

This is an AR study, simulated using a virtual reality (VR), to examine the effects of level of immersion and tracking sensor reliability in AR.  We analyze participant performance on a target following task in which the AR interface provides X-ray vision to help track a moving target.  We varied the field of view of the AR display, as well as the reliability of the head tracking sensor.  In low reliability conditions, we simulate tracker failure by disabling the augmented view of the scene for brief periods.  Our study gives insight into the effect of tracking sensor reliability on user performance in a target following task, as well as the relationship between reliability and field of view in an AR system.

>>>>

\title{Evaluating the Effects of Tracker Reliability and Field of View on a Target Following Task in Augmented Reality}

@@

We examine the effects of level of immersion and tracking sensor reliability in augmented reality (AR) X-ray vision with a virtual reality (VR) based simulation.  We analyze participant performance on a target following task while varying the field of view of the AR display, as well as the reliability of the head tracking sensor.  In low reliability conditions, we simulate sensor dropouts by disabling the augmented view of the scene for brief time periods.  Our study gives insight into the effect of tracking sensor reliability on user performance in a target following task, as well as the relationship between sensor reliability and field of view in an AR system.
